---
title: \assignmentTitle
mainfont: Linux Libertine O
header-includes:
  \newcommand*{\assignmentTitle}{Geographic Range Size}
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_knit$set(eval.after = "fig.cap")
```

<!-- Have to be defined here so they can be used in LaTex header. -->
<!-- First page header -->
\newcommand{\stuName}{`r input$student_name`} 
<!-- Last page footer -->
\newcommand{\firstFancyfoot}{{\footnotesize Report generated `r format(Sys.time(), "%a %d %B %Y %X")`}}
\thispagestyle{first_page}

\subsection*{\assignmentTitle}

\subsubsection{Range Size: North America}


\begin{enumerate}
\begin{multicols}{2}
\item \label{na_predict} \textbf{What do you predict?} Considering all of North America, tell
whether you think most species in a closely related group of organisms (fishes, mussels, or crayfishes), will most species have small, moderate, or large range sizes?
            The North America data set has 126 watersheds. Consider 
            'small range size' to be fewer than 10-15 watersheds, 'large
            range size' to be more than 75, and 'moderate range size' 
            to be somewhere between. These are arbitrary cutoffs to get 
            you started. You may also predict some combination of the three
            options.

\textbf{You predicted} “`r fix_special_chars(input$predict_na)`”

\columnbreak

\item \textbf{Interpret the pattern.} Describe the pattern that you see in the histogram. Do most
species occur in most watersheds (large range size) or do most species
occur in just a few watersheds (small range size)? Or, is it some
combination of the two? Explain below how the observed
      result supports or falsifies your prediction from question~\ref{na_predict}.

\textbf{You explained} “`r fix_special_chars(input$na_result)`”
 
\end{multicols}

\end{enumerate}

```{r fig.dim=c(6.5,4), echo=FALSE, fig.cap=paste("Histogram of North American", str_to_lower(input$na_taxon), "for geographic range size."), fig.align='left'}
plots$na
```

***

### Range Size: States

\begin{enumerate}[resume]
\begin{multicols}{2}

\item \textbf{What do you predict?} What do you predict for the state level? Will most species have small, moderate, or large range sizes? 

\textbf{You predicted} “`r fix_special_chars(input$predict_state)`”

\columnbreak

\item \textbf{Describe and interpret the histograms.}  Do most
species occur in most watersheds (large range size) or do most species
occur in just a few watersheds (small range size)? Or, is it some
combination of the two?

\textbf{You explained} “`r fix_special_chars(input$state_result)`”

\end{multicols}
\end{enumerate}

```{r fig.dim=c(6.5,4), echo=FALSE, fig.cap=paste("Histogram of", input$state, str_to_lower(input$taxon), "for geographic range size."), fig.align='left'}
plots$state
```

***

### Rapoport's Rule

\begin{enumerate}[resume]
\begin{multicols}{2}

\item \textbf{What do you predict?} Consider these five states (from south to north): Alabama, Tennessee, Kentucky, Illinois, and Wisconsin. Do you think fishes, mussels, or crayfishes will follow Rapoport's Rule for range size and species richness from Alabama north to Wisconsin? It is okay for you to say that all, some, or none of these taxonomic groups will agree.  If you think only some taxa will
follow Rapoport's Rule, be sure to identify those taxa in your prediction.

\textbf{You predicted} “`r fix_special_chars(input$predict_rapo_five)`”

\columnbreak

\item \textbf{Do the results agree with your prediction? Explain.}

\textbf{You explained} “`r fix_special_chars(input$rapo_five_result)`”

\end{multicols}
\end{enumerate}

```{r fig.dim=c(6.5,4), echo=FALSE, fig.cap=paste("Species richness of", str_to_lower(input$rapo_taxon), "for five states."), fig.align='left'}
plots$rapo
```


***
\textbf{Your summary} of lessons learned from this exercise.

`r fix_special_chars(input$summary)`

<!-- Time stamp the report -->
\thispagestyle{last_page}
