---
title: \assignmentTitle
#output:
#  pdf_document:
#    latex_engine: lualatex
mainfont: Linux Libertine O
header-includes:
  \newcommand*{\assignmentTitle}{Distribution of species richness}
---
```{r setup, include=FALSE, echo=FALSE}
knitr::opts_knit$set(eval.after = "fig.cap")
```

<!-- Have to be defined here so they can be used in LaTex header. -->
<!-- First page header -->
\newcommand{\stuName}{`r input$student_name`} 
<!-- Last page footer -->
\newcommand{\firstFancyfoot}{{\footnotesize Report generated `r format(Sys.time(), "%a %d %B %Y %X")`}}
\thispagestyle{first_page}

\subsection*{\assignmentTitle}

\subsubsection{North American Taxa}

\begin{enumerate}
\begin{multicols}{2}
\item \textbf{Write your prediction here.} Considering all of North America, tell
whether you think most species in a closely related group of organisms
have large, medium or small range size, or some combination. 

\columnbreak

\textbf{You predicted} "`r input$predict_na`"
 
\end{multicols}

\end{enumerate}

\begin{enumerate}[resume]

\begin{multicols}{2}
\item \textbf{Interpret the pattern.} Describe the pattern that you see. Do most
species occur in most watersheds (large range size) or do most species
occur in just a few watersheds (small range size)? Or, is it some
combination of the two? Explain how the observed result supports or
falsifies your hypothesis in question 1.

\columnbreak

`r input$na_result`

\end{multicols}

\end{enumerate}

```{r fig.dim=c(3,2), echo=FALSE, fig.cap=paste("Histogram of North American", input$na_taxon, "for geographic range size."), fig.align='left'}
plots$na
```

***

### State

For `r paste(input$state, input$taxon)`, you predicted *`r input$predict_state`*

Histogram of `r paste(input$state, input$taxon)` for geographic range size.

```{r fig.dim=c(3,2), echo=FALSE}
plots$state
```

Based on these results, you explained *`r input$state_result`.*

***

For California marine fishes, you predicted *`r input$predict_ca`*

Histogram of California Marine Fishes for geographic range size.

```{r fig.dim=c(3,2), echo=FALSE}
plots$ca
```

Based on these results, you explained *`r input$ca_result`.*

***

At the end, require students to write a summary of what they learned.

<!-- Time stamp the report -->
\thispagestyle{last_page}
