---
title: \assignmentTitle
mainfont: Linux Libertine O
header-includes:
  \newcommand*{\assignmentTitle}{Distribution of species richness}
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_knit$set(eval.after = "fig.cap")
```

<!-- Have to be defined here so they can be used in LaTex header. -->
<!-- First page header -->
\newcommand{\stuName}{`r input$student_name`} 
<!-- Last page footer -->
\newcommand{\firstFancyfoot}{{\footnotesize Report generated `r format(Sys.time(), "%a %d %B %Y %X")`}}
\thispagestyle{first_page}

\subsection*{\assignmentTitle}

\subsubsection{North American Taxa}


\begin{enumerate}
\begin{multicols}{2}
\item \label{na_predict} \textbf{What do you predict?} Considering all of North America, tell
whether you think most species in a closely related group of organisms
have large, medium or small range size, or some combination.

\textbf{You predicted} “`r input$predict_na`”

\columnbreak

\item \textbf{Interpret the pattern.} Describe the pattern that you see. Do most
species occur in most watersheds (large range size) or do most species
occur in just a few watersheds (small range size)? Or, is it some
combination of the two? Explain how the observed result supports or
falsifies your hypothesis in question~\ref{na_predict}.

\textbf{You explained} “`r input$na_result`”
 
\end{multicols}

\end{enumerate}

```{r fig.dim=c(3,2), echo=FALSE, fig.cap=paste("Histogram of North American", input$na_taxon, "for geographic range size."), fig.align='left'}
plots$na
```

***

### State

\begin{enumerate}[resume]
\begin{multicols}{2}

\item \textbf{What do you predict?} For the state you were assigned, 
tell whether you think most species in a closely related
group of organisms have large, medium or small range size, or some
combination.

\textbf{You predicted} “`r input$predict_state`”

\columnbreak

\item \textbf{Interpret and explain the pattern.} Describe the pattern that you see. Do most
species occur in most watersheds (large range size) or do most species
occur in just a few watersheds (small range size)? Or, is it some
combination of the two?

\textbf{You explained} “`r input$state_result`”

\end{multicols}
\end{enumerate}

```{r fig.dim=c(3,2), echo=FALSE, fig.cap=paste("Histogram of", input$state, input$taxon, "for geographic range size."), fig.align='left'}
plots$state
```

***

### California

\begin{enumerate}[resume]
\begin{multicols}{2}

\item \textbf{What do you predict?} For California coastal marine fishes, 
tell whether you think most species in a closely related
group of organisms have large, medium or small range size, or some
combination. ADD SOMETHING ABOUT LATITUDE FOR THEM TO THINK ABOUT.

\textbf{You predicted} “`r input$predict_ca`”

\columnbreak

\item \textbf{Interpret and explain the pattern.} Describe the pattern that you see. Do most
species occur across many degrees of latitude (say, 40° or more of latitude is large range size) or do most species
occur across just a few degrees of latitude (say, 10° or less of latitude is mall range size)? Or, is it some
combination of the two?

\textbf{You explained} “`r input$ca_result`”

\end{multicols}
\end{enumerate}


```{r fig.dim=c(3,2), echo=FALSE, fig.cap="Histogram of California Marine Fishes for geographic range size.", fig.align='left'}
plots$ca
```

***

\textbf{Your summary} of lessons learned from this exercise.

`r input$summary`

<!-- Time stamp the report -->
\thispagestyle{last_page}
