---
title: \assignmentTitle
mainfont: Linux Libertine O
header-includes:
  \newcommand*{\assignmentTitle}{Climate and Ecosystems}
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_knit$set(eval.after = "fig.cap")
```

<!-- Have to be defined here so they can be used in LaTex header. -->
<!-- First page header -->
\newcommand{\stuName}{`r input$student_name`} 
<!-- Last page footer -->
\newcommand{\firstFancyfoot}{{\footnotesize Report generated `r format(Sys.time(), "%a %d %B %Y %X")`}}
\thispagestyle{first_page}

\subsection*{\assignmentTitle}

<!-- \subsubsection{Climate and Ecosystems} -->


\begin{enumerate}
\begin{multicols}{2}
\item \label{na_predict} \textbf{What do you predict?} Which ecosystem
requires the warmest mean annual temperatures? Which ecosystem requires 
the coolest mean annual temperature? Which ecosystem requires the least
amount of precipitation? Which ecosystem requires the most precipitation?
Will any ecosystems co-occur? That is, will they require the same range of temperature \emph{and} precipitation?

\textbf{You predicted} “`r fix_special_chars(input$predict_tutorial)`”

\columnbreak

\item \textbf{Interpret the scatterplot.} Do the results agree with your 
predictions? Did you successfully predict which species requires warmer or 
cooler temperatures, or less precipitation? Describe the pattern you see in 
the scatterplot.

\textbf{You explained} “`r fix_special_chars(input$interpret_result)`”
 
\end{multicols}

\end{enumerate}

```{r fig.dim=c(6.5,4), echo=FALSE, fig.cap=paste("Relationship of three ecosystems with two climate variables."), fig.align='left'}
plots$na
```

***

\textbf{Your summary} of lessons learned from this exercise.

`r fix_special_chars(input$summary)`


<!-- Time stamp the report 
\AtEndDocument{\thispagestyle{last_page}} -->
