---
title: \assignmentTitle
mainfont: Linux Libertine O
header-includes:
  \newcommand*{\assignmentTitle}{Climate and Ecosystems}
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_knit$set(eval.after = "fig.cap")
```

<!-- Have to be defined here so they can be used in LaTex header. -->
<!-- First page header -->
\newcommand{\stuName}{`r input$student_name`} 
<!-- Last page footer -->
\newcommand{\firstFancyfoot}{{\footnotesize Report generated `r format(Sys.time(), "%a %d %B %Y %X")`}}
\thispagestyle{first_page}

\subsection*{\assignmentTitle}

<!-- \subsubsection{Climate and Ecosystems} -->


\begin{enumerate}
\begin{multicols}{2}
\item \label{na_predict} \textbf{What do you predict?} Which ecosystem
requires the warmest mean annual temperatures? Which ecosystem requires 
the coolest mean annual temperature? Which ecosystem requires the least
amount of precipitation? Which ecosystem requires the most precipitation?
Will any ecosystems co-occur? That is, will they require the same range of temperature \emph{and} precipiation?

\textbf{You predicted} “`r input$predict_tutorial`”

\columnbreak

\item \textbf{Interpret the scatterplot.} Do ? Or, is it some
combination of the two? Explain how the observed result supports or
falsifies your hypothesis in question~\ref{na_predict}.

\textbf{You explained} “`r input$na_result`”
 
\end{multicols}

\end{enumerate}

```{r fig.dim=c(6,4), echo=FALSE, fig.cap=paste("Relationship of three ecosystems with two climate variables."), fig.align='left'}
plots$na
```

***

<!--
### State

\begin{enumerate}[resume]
\begin{multicols}{2}

\item \textbf{What do you predict?} For the state you were assigned, 
tell whether you think most species in a closely related
group of organisms have large, medium or small range size, or some
combination.

\textbf{You predicted} “`r input$predict_state`”

\columnbreak

\item \textbf{Interpret and explain the pattern.} Describe the pattern that you see. Do most
species occur in most watersheds (large range size) or do most species
occur in just a few watersheds (small range size)? Or, is it some
combination of the two?

\textbf{You explained} “`r input$state_result`”

\end{multicols}
\end{enumerate}

```{r fig.dim=c(3,2), echo=FALSE, fig.cap=paste("Histogram of", input$state, input$taxon, "for geographic range size."), fig.align='left'}
plots$state
```

***

### California

\begin{enumerate}[resume]
\begin{multicols}{2}

\item \textbf{What do you predict?} For California coastal marine fishes, 
tell whether you think most species in a closely related
group of organisms have large, medium or small range size, or some
combination. ADD SOMETHING ABOUT LATITUDE FOR THEM TO THINK ABOUT.

\textbf{You predicted} “`r input$predict_ca`”

\columnbreak

\item \textbf{Interpret and explain the pattern.} Describe the pattern that you see. Do most
species occur across many degrees of latitude (say, 40° or more of latitude is large range size) or do most species
occur across just a few degrees of latitude (say, 10° or less of latitude is mall range size)? Or, is it some
combination of the two?

\textbf{You explained} “`r input$ca_result`”

\end{multicols}
\end{enumerate}


```{r fig.dim=c(3,2), echo=FALSE, fig.cap="Histogram of California Marine Fishes for geographic range size.", fig.align='left'}
plots$ca
```

***
-->

\textbf{Your summary} of lessons learned from this exercise.

`r input$summary`


<!-- Time stamp the report 
\AtEndDocument{\thispagestyle{last_page}} -->
