---
title: \assignmentTitle
mainfont: Linux Libertine O
header-includes:
  \newcommand*{\assignmentTitle}{California Coastal Marine Fishes}
---


```{r setup, include=FALSE, echo=FALSE}
knitr::opts_knit$set(eval.after = "fig.cap")
```

<!-- Have to be defined here so they can be used in LaTex header. -->
<!-- First page header -->
\newcommand{\stuName}{`r input$student_name`} 
<!-- Last page footer -->
\newcommand{\firstFancyfoot}{{\footnotesize Report generated `r format(Sys.time(), "%a %d %B %Y %X")`}}
\thispagestyle{first_page}

\subsection*{\assignmentTitle}

\subsubsection{Range Size}


\begin{enumerate}
\begin{multicols}{2}

\item \label{ca_predict} \textbf{What is your prediction?} Given that the total latitudinal range in the data set covers 99° of latitude, from 30°S to 68°N, does the mean number of degrees latitude occupied suggest that most coastal marine fishes likely have large (many degrees of latitude) or small range size (a few degrees of latitude)? Explain.


For comparison, Missouri from south (bottom of the bootheel) to north (Iowa
border) spans about 4.5° of latitude.

\textbf{You predicted} “`r fix_special_chars(input$predict_ca_range)`”

\columnbreak

\item \textbf{Where will species richness be highest?} 
The data set spans from tropical regions south of the equator to north of the Arctic Circle. In general terms, where do you think
            species richness (number of species) will be highest? You
            do not have to give an exact latitude, but you can enter things
            like “close to the equator”, or “at the higher latitudes.” Remember that
            all species in the data set occur at least partially in California.

\textbf{You explained} “`r fix_special_chars(input$ca_result)`”
 
\end{multicols}

\end{enumerate}

```{r fig.dim=c(6.5,4), echo=FALSE, fig.cap=paste("Histogram of California coastal marine fishes for geographic range size."), fig.align='left'}
plots$ca
```

***

### Point Conception

\begin{enumerate}[resume]
\begin{multicols}{2}

\item \textbf{Where will species richness be highest?} 
The data set spans from tropical regions south of the equator to north of the Arctic Circle. 
In general terms, where do you think species richness (number of species) will be highest? 
You do not have to give an exact latitude, but you can enter things like “close to the 
equator”, or “at the higher latitudes.” Remember that all species in the data set occur at
least partially in California.

\textbf{You predicted} “`r fix_special_chars(input$predict_pc)`”

\columnbreak

\item \textbf{Interpret and explain the pattern.} Describe the pattern that you see. Do most
species occur across many degrees of latitude (say, 40° or more of latitude is large range size) or do most species
occur across just a few degrees of latitude (say, 10° or less of latitude is mall range size)? Or, is it some
combination of the two?

\textbf{You explained} “`r fix_special_chars(input$pc_result)`”

\end{multicols}
\end{enumerate}


```{r fig.dim=c(6.5,4), echo=FALSE, fig.cap="Dot plot showing species richness for each degree of latitude from 30°S to 68°N.", fig.align='left'}
plots$pc
```

***

\textbf{Your summary} of lessons learned from this exercise.

`r fix_special_chars(input$summary)`

<!-- Time stamp the report -->
\thispagestyle{last_page}
