---
title: \assignmentTitle
mainfont: Linux Libertine O
header-includes:
  \newcommand*{\assignmentTitle}{Introduction to cluster and \textsc{nmds} analyses}
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_knit$set(eval.after = "fig.cap")
```

<!-- Have to be defined here so they can be used in LaTex header. -->
<!-- First page header -->
\newcommand{\stuName}{`r input$student_name`} 
<!-- Last page footer -->
\newcommand{\firstFancyfoot}{{\footnotesize Report generated `r format(Sys.time(), "%a %d %B %Y %X")`}}
\thispagestyle{first_page}

\subsection*{\assignmentTitle}

\begin{multicols}{2}
Cluster and \textsc{nmds} are two useful analytical techniques to explore
biogeographic provinces and ecoregions. For this exercise, you will use a
dataset of 53 species of freshwater fishes that live in Montana's 10 watersheds (right). The watersheds span across Montana's eastern Great Plains and
western Rocky Mountains. The mountains are divided by the 
\textbf{continental divide}. Watersheds east of the divide flow to the Atlantic
Ocean. Watersheds west of the divide flow west to the Pacific Ocean. 

\columnbreak

\includegraphics[width=0.95\linewidth]{`r paste0(tempdir(),"/montana_watersheds.png")`}

\end{multicols}

\begin{enumerate}
\begin{multicols}{2}
\item `r predictions_question1`

\textbf{You predicted} “`r fix_special_chars(input$predictions_question1)`”

\item `r predictions_question2`

\textbf{You explained} “`r fix_special_chars(input$predictions_question2)`”

\item `r cluster_question1`

\textbf{You explained} “`r fix_special_chars(input$cluster_question1)`”

\item `r nmds_question1`

\textbf{You explained} “`r fix_special_chars(input$nmds_question1)`”

\end{multicols}

\end{enumerate}

```{r fig.dim=c(6.5,4), echo=FALSE, fig.cap=paste("Cluster (left) and \\textsc{nmds} (right) plots showing similarity of Montana watersheds based on similarity of fish fauna."),  fig.show='hold', out.width="49%"}
plots$cluster
plots$nmds
```

***

`r fix_special_chars(input$summary)`

<!-- Time stamp the report 
\thispagestyle{last_page}-->
