---
title: \assignmentTitle
mainfont: Linux Libertine O
header-includes:
  \newcommand*{\assignmentTitle}{Introduction to Cluster and NMDS analyses}
---


```{r setup, include=FALSE, echo=FALSE}
knitr::opts_knit$set(eval.after = "fig.cap")
```

<!-- Have to be defined here so they can be used in LaTex header. -->
<!-- First page header -->
\newcommand{\stuName}{`r input$student_name`} 
<!-- Last page footer -->
\newcommand{\firstFancyfoot}{{\footnotesize Report generated `r format(Sys.time(), "%a %d %B %Y %X")`}}
\thispagestyle{first_page}

\subsection*{\assignmentTitle}

### Introduction and Predictions


\begin{enumerate}
\begin{multicols}{2}
\item `r predictions_question1`

\textbf{You predicted} “`r fix_special_chars(input$predictions_question1)`”

\item `r predictions_question2`

\textbf{You explained} “`r fix_special_chars(input$predictions_question2)`”

\item `r cluster_question1`

\textbf{You explained} “`r fix_special_chars(input$cluster_question1)`”

\item `r nmds_question1`

\textbf{You explained} “`r fix_special_chars(input$nmds_question1)`”

\end{multicols}

\end{enumerate}

```{r fig.dim=c(6.5,4), echo=FALSE, fig.cap=paste("Species richness or relative area per degree of latitude in the U.S."), fig.align='left'}
plots$cluster
```

***

`r fix_special_chars(input$summary)`

<!-- Time stamp the report -->
\thispagestyle{last_page}
