---
title: \assignmentTitle
mainfont: Linux Libertine O
header-includes:
  \newcommand*{\assignmentTitle}{Rapoport‘s Rule}
---


```{r setup, include=FALSE, echo=FALSE}
knitr::opts_knit$set(eval.after = "fig.cap")
```

<!-- Have to be defined here so they can be used in LaTex header. -->
<!-- First page header -->
\newcommand{\stuName}{`r input$student_name`} 
<!-- Last page footer -->
\newcommand{\firstFancyfoot}{{\footnotesize Report generated `r format(Sys.time(), "%a %d %B %Y %X")`}}
\thispagestyle{first_page}

\subsection*{\assignmentTitle}

### Rapoport's Rule: Richness and relative area for North American fishes


\begin{enumerate}
\begin{multicols}{2}
\item \label{richness_area_predict} \textbf{What do you predict for species richness?} 
Based on what you have learned so far from lecture and other exercises, do you think
freshwater fishes of the U.S. will follow Rapoport's Rule for species richness? Do you think
species richness could be higher at mid-U.S. latitudes compared to lower or higher latitudes
in the U.S.? Explain.

\textbf{You predicted} “`r fix_special_chars(input$predict_richness_area)`”

\item \textbf{At what latitudes, approximately, are mean and maximum species richness the highest? Does this agree with range area? Explain.}.

\textbf{You explained} “`r fix_special_chars(input$richness_area_q1)`”

\item \textbf{Does species richness and area for North American freshwater
        fishes follow Rapoport's Rule? Explain.}

\textbf{You explained} “`r fix_special_chars(input$richness_area_q2)`”

\item \textbf{Why do you think species richness is relatively low between 24–28°N compared to between 30–38°N? The map below left (scroll down if necessary) should help you think about this.}

\textbf{You explained} “`r fix_special_chars(input$richness_area_q3)`”

\end{multicols}

\end{enumerate}

```{r fig.dim=c(6.5,4), echo=FALSE, fig.cap=paste("Species richness or relative area per degree of latitude in the U.S."), fig.align='left'}
plots$rapo
```

***

### Rapoport's Rule: Range size for North American fishes

\begin{enumerate}[resume]
\begin{multicols}{2}

\item \textbf{What do you predict for range size?} Based on what you have learned so far 
from lecture and other exercises, do you think range size of freshwater fishes will strictly
follow Rapoport's Rule for range size as you go from south to north? Why or why not? Do you
think there might be differences in the south to north trend if you compare the eastern U.S.
to the western U.S.? Why or why not?

\textbf{You predicted} “`r fix_special_chars(input$predict_pc)`”

\item \textbf{Based on this figure, combined with the previous graphs,  do U.S. freshwater fishes follow Rapoport’s Rule for geographic range size? Explain.}

\textbf{You explained} “`r fix_special_chars(input$pc_q4)`”

\item \textbf{Considering the geographic ranges east of the Rocky 
Mountains, what region of the U.S. seems to have most of the smaller bubbles? Why do you think this is?}

\textbf{You wrote} “`r fix_special_chars(input$pc_q5)`”

\item \textbf{What geographic region west of the Rocky Mountains seems
to have the fewest bubbles? (Or, most of the smallest bubbles?) Why do you think this is?}

\textbf{You wrote} “`r fix_special_chars(input$pc_q6)`”

\end{multicols}
\end{enumerate}


```{r fig.dim=c(6.5,5), echo=FALSE, fig.cap="Relative geographic area occupied by North American freshwater fishes. Circle diamter is proportional to square degrees of area occupied by each species.", fig.align='left'}
plots$pc
```

***

\textbf{Your summary} of lessons learned from this exercise.

`r fix_special_chars(input$summary)`

<!-- Time stamp the report -->
\thispagestyle{last_page}
