---
title: \assignmentTitle
mainfont: Linux Libertine O
header-includes:
  \newcommand*{\assignmentTitle}{Rapoport‘s Rule}
---


```{r setup, include=FALSE, echo=FALSE}
knitr::opts_knit$set(eval.after = "fig.cap")
```

<!-- Have to be defined here so they can be used in LaTex header. -->
<!-- First page header -->
\newcommand{\stuName}{`r input$student_name`} 
<!-- Last page footer -->
\newcommand{\firstFancyfoot}{{\footnotesize Report generated `r format(Sys.time(), "%a %d %B %Y %X")`}}
\thispagestyle{first_page}

\subsection*{\assignmentTitle}

### Rapoport's Rule: Richness and relative area for North American fishes


\begin{enumerate}
\begin{multicols}{2}
\item \label{richness_area_predict} \textbf{What do you predict?} Considering all of North America, tell
whether you think most species in a closely related group of organisms
have large, medium or small range size, or some combination.

\textbf{You predicted} “`r fix_special_chars(input$predict_richness_area)`”

\item \textbf{At what latitudes, approximately, are mean and maximum species richness the highest? Does this agree with range area? Explain.}.

\textbf{You explained} “`r fix_special_chars(input$richness_area_q1)`”

\item \textbf{Does species richness and area for North American freshwater
        fishes follow Rapoport's Rule? Explain.}

\textbf{You explained} “`r fix_special_chars(input$richness_area_q2)`”

\item \textbf{Why do you think species richness is relatively low between 24–28°N compared to between 30–38°N? The map below left (scroll down if necessary) should help you think about this.}

\textbf{You explained} “`r fix_special_chars(input$richness_area_q3)`”

\end{multicols}

\end{enumerate}

```{r fig.dim=c(6.5,4), echo=FALSE, fig.cap=paste("Species richness or relative area per degree of latitude in the U.S."), fig.align='left'}
plots$rapo
```

***

### Rapoport's Rule: Range size for North American fishes

\begin{enumerate}[resume]
\begin{multicols}{2}

\item \textbf{What do you predict?} For California coastal marine fishes, 
tell whether you think most species in a closely related
group of organisms have large, medium or small range size, or some
combination. ADD SOMETHING ABOUT LATITUDE FOR THEM TO THINK ABOUT.

\textbf{You predicted} “`r fix_special_chars(input$predict_pc)`”

\item \textbf{Interpret and explain the pattern.} Describe the pattern that you see. Do most
species occur across many degrees of latitude (say, 40° or more of latitude is large range size) or do most species
occur across just a few degrees of latitude (say, 10° or less of latitude is mall range size)? Or, is it some
combination of the two?

\textbf{You explained} “`r fix_special_chars(input$pc_result)`”

\item \textbf{Based on this figure, combined with the previous graphs,  do U.S. freshwater fishes follow Rapoport’s Rule for geographic range size? Explain.}

\textbf{You explained} “`r fix_special_chars(input$pc_q4)`”

\item \textbf{Considering the geographic ranges east of the Rocky 
Mountains, what region of the U.S. seems to have most of the smaller bubbles? Why do you think this is?}

\textbf{You wrote} “`r fix_special_chars(input$pc_q5)`”

\item \textbf{What geographic region west of the Rocky Mountains seems
to have the fewest bubbles? (Or, most of the smallest bubbles?) Why do you think this is?}

\textbf{You wrote} “`r fix_special_chars(input$pc_q6)`”

\end{multicols}
\end{enumerate}


```{r fig.dim=c(6.5,5), echo=FALSE, fig.cap="Relative geographic area occupied by North American freshwater fishes. Circle diamter is proportional to square degrees of area occupied by each species.", fig.align='left'}
plots$pc
```

***

\textbf{Your summary} of lessons learned from this exercise.

`r fix_special_chars(input$summary)`

<!-- Time stamp the report -->
\thispagestyle{last_page}
